Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections

### 2022-05-19 figures/approach.tex
minor edits [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2354476139

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20cm} 
    \newcommand{\figheight}{15cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,14.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
\draw [densely dotted, red,thick] (3,14.5) -- (3,10);
\draw [densely dotted, red,thick] (3,9.2) -- (3,6.4);

@@

\draw (3.55,10.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
\draw (4.15,10.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
\draw [dimen] (D1) -- (D2) node {$D_{Beam}$};

\draw [->, very thick] (3,10) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$IS_X$} ;
\draw [->, very thick] (S1) -- (3.85,10.4) node[midway,below right] {$IS_Y$};

\node (anchor) at (6.0,14.35) {}; 
\node[labelNode] {B};

% Place nodes
\node [block] (init) at (8.0,13.35) {\textbf{START} \\ Collect overview image};
\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};

@@

\node (anchor) at (11.5,14.35) {}; 
\node[labelNode] {C};
\node[graphicNode] {\includegraphics[width=8cm]{content/images/ac_strategy.png}};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (0.5,4.5) {}; 
\node[labelNode] {C};
\node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
\node[above = 0cm and 0cm of euc.north] {Eucentric Focus};

\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (5.5,4.5) {}; 
\node[labelNode] {D};
\node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
\node[above = 0cm and 0cm of fff.north] {Fringe-free Focus};
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (10.5,4.5) {}; 
\node[labelNode] {E};
\node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};

    \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};
    \end{tikzpicture}
    \end{document}

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{calc}
    \def\centerarc[#1](#2)(#3:#4:#5){ \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
    \usetikzlibrary{3d}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,9.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
\draw [densely dotted, red,thick] (3,9.5) -- (3,5.0);
\draw [densely dotted, red,thick] (3,4.2) -- (3,1.4);

@@

\draw (3.55,5.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
\draw (4.15,5.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
\draw [dimen] (D1) -- (D2) node {$D_{Beam}$};

\draw [->, very thick] (3,5) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$BIS_X$} ;
\draw [->, very thick] (S1) -- (3.85,5.4) node[midway,below right] {$BIS_Y$};

\node (anchor) at (6.0,9.35) {}; 
\node[labelNode] {B};

% Place nodes
\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};

@@

\node (anchor) at (11.5,9.35) {}; 
\node[labelNode] {C};
% X axis is 9.4um
\node[graphicNode] (image) {\includegraphics[width=8cm]{content/code/img/acquisition_positions.png}};
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.35cm, yshift=0.3cm]image.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.35cm, yshift=0.3cm]image.south west);
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (0.5,-0.5) {}; 
\node[labelNode] {D};
\node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
\node[anchor=center] at ([shift={(0.0cm,0.3cm)}]euc.north) {Eucentric Focus};
\draw [line width=1.25mm,white] ([xshift=-0.05cm, yshift=0.1cm]euc.south east) -- ([xshift=-0.8cm, yshift=0.1cm]euc.south east);
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (5.5,-0.5) {}; 
\node[labelNode] {E};
\node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
\node[anchor=center] at ([shift={(0.0cm,0.3cm)}]fff.north) {Fringe-free Focus};
\draw [line width=1.25mm,white] ([xshift=-0.05cm, yshift=0.1cm]fff.south east) -- ([xshift=-0.8cm, yshift=0.1cm]fff.south east);
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (10.5,-0.5) {}; 
\node[labelNode] {F};
\node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};
    \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};
    \end{tikzpicture}
    \end{document}

### 2022-05-19 figures/assembly.tex
minor edits [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2354476139

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{calc}
    \def\centerarc[#1](#2)(#3:#4:#5){ \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
    \usetikzlibrary{3d}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \node (anchor) at (0.5,9.35) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[width=5cm]{content/graphics/approach/approach.png}};
\draw [densely dotted, red,thick] (3,9.5) -- (3,5.0);
\draw [densely dotted, red,thick] (3,4.2) -- (3,1.4);

\tikzset{dimen/.style={<->,>=latex,thin,every rectangle node/.style={above right=0.2cm and -0.3cm,fill=white,midway,font=\sffamily}}}

\draw (3.55,5.4) -- ++(0,1.5) coordinate (D1) -- +(0,5pt);
\draw (4.15,5.4) -- ++(0,1.5) coordinate (D2) -- +(0,5pt);
\draw [dimen] (D1) -- (D2) node {$D_{Beam}$};

\draw [->, very thick] (3,5) -- ++(0.5,-0.2)  coordinate (S1) node[midway,below left] {$BIS_X$} ;
\draw [->, very thick] (S1) -- (3.85,5.4) node[midway,below right] {$BIS_Y$};

\node (anchor) at (6.0,9.35) {}; 
\node[labelNode] {B};

% Place nodes
\node [block] (init) at (8.0,8.35) {\textbf{START} \\ Collect overview image};
\node [block, below = 0.3cm of init.south] (identify) {Setup hexagonal grid covering lamella area};
\node [block, below = 0.3cm of identify.south] (mutate) {Beam-imageshift to tile n=i};
\node [block, below = 0.3cm of mutate.south] (transfer) {Capture exposure and determine defocus by CTF fitting};
\node [block, below = 0.3cm of transfer.south] (evaluate) {Adjust defocus by difference between expected and measured value};

% Draw edges
\path [line] (init) -- (identify);
\path [line] (identify) -- (mutate);
\path [line] (mutate) -- (transfer);
\path [line] (transfer) -- (evaluate);
\path [line] (evaluate) -|  ([xshift=0.5cm, yshift=0cm]transfer.east) |- (mutate);

\node (anchor) at (11.5,9.35) {}; 
\node[labelNode] {C};
% X axis is 9.4um
\node[graphicNode] (image) {\includegraphics[width=8cm]{content/code/img/acquisition_positions.png}};
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.35cm, yshift=0.3cm]image.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.35cm, yshift=0.3cm]image.south west);
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (0.5,-0.5) {}; 
\node[labelNode] {D};
\node[graphicNode] (euc) {\includegraphics[height=4.0cm]{content/images/fringebeam.png}};
\node[anchor=center] at ([shift={(0.0cm,0.3cm)}]euc.north) {Eucentric Focus};
\draw [line width=1.25mm,white] ([xshift=-0.05cm, yshift=0.1cm]euc.south east) -- ([xshift=-0.8cm, yshift=0.1cm]euc.south east);
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (5.5,-0.5) {}; 
\node[labelNode] {E};
\node[graphicNode] (fff) {\includegraphics[height=4.0cm]{content/images/nofringebeam.png}};
\node[anchor=center] at ([shift={(0.0cm,0.3cm)}]fff.north) {Fringe-free Focus};
\draw [line width=1.25mm,white] ([xshift=-0.05cm, yshift=0.1cm]fff.south east) -- ([xshift=-0.8cm, yshift=0.1cm]fff.south east);
\iftoggle{draft}{\node [redAnchorNode] {};};

\node (anchor) at (10.5,-0.5) {}; 
\node[labelNode] {F};
\node[anchor=north west, below right=-0.5cm and 0cm of anchor] {\includegraphics[height=4.8cm]{content/code/img/defocusplot.pdf}};
\iftoggle{draft}{\node [redAnchorNode] {};};
    \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};
    \end{tikzpicture}
    \end{document}

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{calc}
    \def\centerarc[#1](#2)(#3:#4:#5){ \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
    \usetikzlibrary{3d}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{15cm} 
    \newcommand{\figheight}{5cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

    \def\panelheight{6.0cm}

\node (anchor) at (0.5,13.0) {}; 
\node[labelNode] {A};
\node[graphicNode] (img) {\includegraphics[height=\panelheight,trim=0.0 0 0cm 0, clip]{content/images/euc_lamella1_view.png}};
% Title
\node[anchor=center,align=center] at ([shift={(0.0cm,0.6cm)}]img.north) {\baselineskip=8pt   \\ 38Å pixel size \\ 300μm defocus};
% scalebar - physical height is 12810 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 12.81 , yshift=0.3cm]img.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 12.81, yshift=0.3cm]img.south west);

\node (anchor) at (5.5,13.0) {}; 
\node[labelNode] {B};
\node[graphicNode] (img) {\includegraphics[height=6.0cm,trim=0 0 0cm 0, clip]{content/images/euc_lamella1_assm.png}};
\node[anchor=center,align=center] at ([shift={(0.0cm,0.7cm)}]img.north) {\baselineskip=8pt Eucentric Focus \\ 1.76Å pixel size \\ 800nm defocus};
% Red Box
\node (rect) at (6.52,10.78) [anchor=center,draw,thick,minimum width=0.375cm,minimum height=0.469cm,color=red] {};
% scalebar - physical height is 12810 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 12.81 , yshift=0.3cm]img.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 12.81, yshift=0.3cm]img.south west);

\node (anchor) at (10.6,13.0) {}; 
\node[labelNode] {C};
% height is 750 nm
\node[graphicNode] (image) {\includegraphics[height=6.0cm]{content/images/euc_lam1_zoomin.png}};
\node (n3) [box=red, fit=(image)] {};
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.3cm, yshift=0.3cm]image.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.3cm, yshift=0.3cm]image.south west);

\node (anchor) at (0.5,5.0) {}; 
\node[labelNode] {D};
\node[graphicNode] (img) {\includegraphics[height=6.0cm,trim=0 0 0cm 0, clip]{content/images/fff_lamella4_view.png}};
\node[anchor=center,align=center] at ([shift={(0.0cm,0.6cm)}]img.north) {\baselineskip=8pt  \\ 38Å pixel size \\ 300μm defocus};
% scalebar - physical height is 9337.5 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 9.3375 , yshift=0.3cm]img.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 9.3375, yshift=0.3cm]img.south west);

\node (anchor) at (5.8,5.0) {}; 
\node[labelNode] {E};
\node[graphicNode] (img) {\includegraphics[height=6.0cm,trim=0 0 0cm 0, clip]{content/images/fff_lamella4_assm.png}};
\node[anchor=center,align=center] at ([shift={(0.0cm,0.7cm)}]img.north) {\baselineskip=2pt Fringe-free Focus \\ 1.76Å pixel size \\ 800nm defocus};
\node (rect) at (8.438,3.83) [anchor=center,draw,thick,minimum width=0.375cm,minimum height=0.469cm,color=red] {};
% scalebar - physical height is 9337.5 nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 9.3375 , yshift=0.3cm]img.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]img.south west) -- ([xshift=0.5cm + \panelheight / 9.3375, yshift=0.3cm]img.south west);

\node (anchor) at (11.0,5.0) {}; 
\node[labelNode] {F};
% height is 750 nm
\node[graphicNode] (image) {\includegraphics[height=6.0cm]{content/images/fff_lam4_zoomin.png}};
\node (n3) [box=red, fit=(image)] {};
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.3cm, yshift=0.3cm]image.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]image.south west) -- ([xshift=1.3cm, yshift=0.3cm]image.south west);
    \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};
    \end{tikzpicture}
    \end{document}

### 2022-05-19 figures/crop_unblur.tex
minor edits [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2354476139

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20.0cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{calc}
    \def\centerarc[#1](#2)(#3:#4:#5){ \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
    \usetikzlibrary{3d}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{20.0cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

\node (anchor) at ([shift={(0.0,-1.0cm)}]0.5,9.5 |- panel.south east) {}; 
\node[labelNode] {D};
\node[graphicNode] (panel) {\includegraphics[height=5cm]{content/images/deco_unblur/zap000.png}};
\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel2) {\includegraphics[height=5cm]{content/images/deco_unblur/zap002.png}};

\node (anchor) at ([shift={(1.5,0.0cm)}] panel.north east) {}; 
\node[labelNode] {E};
\node[graphicNode] (panel) {\includegraphics[height=5cm]{content/images/deco_unblur/zap001.png}};
\node (anchor) at ([shift={(0.0,-0.5cm)}]panel.south west) {}; 
\node[graphicNode] (panel) {\includegraphics[height=5cm]{content/images/deco_unblur/zap004.png}};

### 2022-05-19 figures/matching_fff.tex
minor edits [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/5f9575bbee2059d4e92d5c821f29682c4a661e49/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2354476139

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{17cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

\node (anchor) at (0.5,9.5) {}; 
\node[labelNode] {A};
\node[graphicNode] {\includegraphics[height=12cm]{content/images/fff_lamella4_1000px.png}};
\node[graphicNode] {\includegraphics[height=12cm]{content/images/fff_lamella4_just_matches.png}};

\node (anchor) at (11.0,9.5) {}; 
\node[labelNode] {B};
\node[anchor=north west, below right=0cm and -4cm of anchor] {\includegraphics[height=12cm]{content/images/fff_lamella4_just_matches_side.png}};

\node (anchor) at (13.0,9.5) {}; 
\node[labelNode] {C};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det3.png}};

\node (anchor) at (13.0,6.5) {}; 
\node[labelNode] {D};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det1.png}};

\node (anchor) at (13.0,3.5) {}; 
\node[labelNode] {E};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det4.png}};

\node (anchor) at (13,0.5) {}; 
\node[labelNode] {F};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_just_matches_det6.png}};

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{calc}
    \def\centerarc[#1](#2)(#3:#4:#5){ \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
    \usetikzlibrary{3d}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{17cm} 
    \newcommand{\figheight}{10cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

\newlength{\panelheight}
\setlength{\panelheight}{12cm}

\node (anchor) at (0.5,9.5) {}; 
\node[labelNode] {A};
\node[graphicNode] (assm) {\includegraphics[height=\panelheight]{content/images/fff_lamella4_assm.png}};
\node[graphicNode] {\includegraphics[height=\panelheight]{content/images/fff_lamella4.png}};
\node (rect) at (5.35,5.5) [anchor=center,draw,thick,minimum width=0.4cm,minimum height=0.4cm,color=red] {};
\node (rect) at (8.05,1.75) [anchor=center,draw,thick,minimum width=0.6cm,minimum height=0.6cm,color=green] {};
\node (rect) at (6.45,-1.23) [anchor=center,draw,thick,minimum width=0.5cm,minimum height=0.5cm,color=blue!60] {};
% scalebar - physical height is 9337.5nm
\draw [line width=1.55mm,white] ([xshift=0.5cm, yshift=0.3cm]assm.south west) -- ([xshift=0.5cm + \panelheight / 9.3375 , yshift=0.3cm]assm.south west);
\draw [line width=0.7mm,black] ([xshift=0.5cm, yshift=0.3cm]assm.south west) -- ([xshift=0.5cm + \panelheight / 9.3375, yshift=0.3cm]assm.south west);

\node (anchor) at (11.0,9.5) {}; 
\node[labelNode] {B};
\node[anchor=north west, below right=0cm and 0.0cm of anchor] (side) {\includegraphics[height=12cm, trim=15.5cm 0 2cm 0]{content/images/fff_lamella4_side.png}};

\draw [->, thick] ($ (assm.east) + (0.1,0) $) -- node[above=0.2cm, align=center] (c) {} ($ (side.west) + (0.2,0) $);

\centerarc [canvas is zx plane at y=0.75, ->](c.center)(-90:180:0.15);
\draw [very thick] ($ (c.center) + (0,-0.1) $) -- ($ (c.center) + (0,0.2) $);
\node at ($ (c.center) + (0.5,0) $) {90°};

\newlength{\panelheightm}
\setlength{\panelheightm}{2.8cm}
\node (anchor) at (13.0,9.5) {}; 
\node[labelNode] {C};
\node[graphicNode] (pan) {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail2.png}};
\node (n3) [box=red, fit=(pan)] {};
% scalebar - physical height is 300 nm
\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3 , yshift=0.2cm]pan.south west);
\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 3, yshift=0.2cm]pan.south west);

\node (anchor) at (13.0,6.5) {}; 
\node[labelNode] {D};
\node[graphicNode] (pan) {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail1.png}};
\node (n3) [box=green, fit=(pan)] {};
% scalebar - physical height is 500 nm
\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 5 , yshift=0.2cm]pan.south west);
\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 5, yshift=0.2cm]pan.south west);

\node (anchor) at (13.0,3.5) {}; 
\node[labelNode] {E};
\node[graphicNode] (pan){\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail3_back.png}};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail3_close.png}};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail3_far.png}};
\node (n3) [box=blue!60, fit=(pan)] {};
% scalebar - physical height is 400 nm
\draw [line width=1.55mm,white] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 4 , yshift=0.2cm]pan.south west);
\draw [line width=0.7mm,black] ([xshift=0.2cm, yshift=0.2cm]pan.south west) -- ([xshift=0.2cm + \panelheightm / 4, yshift=0.2cm]pan.south west);

\node (anchor) at (13,0.5) {}; 
\node[labelNode] {F};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail3_far_side.png}};
\node[graphicNode] {\includegraphics[height=2.8cm]{content/images/fff_lamella4_detail3_close_side.png}};
